Trends of SDR in Thessaloniki

### 2023-07-04 Article.Rmd
Commit 2023-07-04 12:11
Commit 2023-07-04 13:11

```{r echo=F, include=T, warning=FALSE}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/2022_sdr_trends/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")

@@

...... cloud formation occurrences and constitution nuclei. cite.....

@@

The SDR data were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ($40^\circ38'$N, $22^\circ57'$E, 80m a.s.l.).
The monitoring site is located near the city centre.
During the study period the CM-21 pyranometer has been independently calibrated four times.
<!-- Preparation. -->
There are three distinct steps to the creation of this dataset:
a) the acquisition of radiation measurements from the sensors, 
b) a radiation data quality check, and 
c) the identification of "clear sky" conditions from the radiometric data
d) data aggregation and trend analysis.

@@

As global radiation clear sky reference we are using the Haurwitz’s model, adjusted for our site with a factor of `r signif(alpha,3)` (Eq. \ref{eq:ahau}).
The selection of a clear sky reference model, was based on SDR observation from the period 2016 – 2021.
Where, after an iterative optimization of eight simple models (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with different factors.
We found, that Haurwitz’s model, adjusted with a factor of `r signif(alpha,3)` has the lower root mean squared error (RMSE). 
The tried models are described by @Reno2012 and tested by @Reno2016.
The iterative optimization method, for the selection of the reference is discussed by @Long2000 and @Reno2016.

@@

The running max measured value $M_{Gi} = max[\text{SDR}_{i}]$, is compared to a similar constructed value from the reference $M_{CSi} = max[\text{SDR}_{i\text{Clear Sky}}]$ (Eq. \ref{eq:MaxVIP}).

@@

We calculated the SDR trends, from the mean daily values of the departure from the seasonal values, for the whole time series for the three sky conditions (Table \ref{tab:trendtable}).

@@

Analyzing the long term trends of SDR to bins of SZA, we can see the contribution of the geometry and time in a diurnal level (Figures \ref{fig:szatrends}a and \ref{fig:szatrends}b). Although there is a seasonal distribution of SZA than in not presented here.

@@

Figure \ref{fig:cumsum}

@@

similar results with Evidence for Clear‐Sky Dimming and Brightening in Central Europe_Wild2021.pdf
inclue in discusion

>>>>

```{r echo=F, include=T, warning=FALSE, message=FALSE}
res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("~/MANUSCRIPTS/2022_sdr_trends/data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/2022_sdr_trends/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")

@@

...... cloud formation occurrences and constitution nuclei. cite .....

@@

The SDR data were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ($40^\circ38'$N, $22^\circ57'$E, 80m\ a.s.l.).
The monitoring site is located near the city centre.
During the study period the CM-21 pyranometer has been independently calibrated four times.
<!-- Preparation. -->
There are three distinct steps to the creation of this dataset:
a)\ the acquisition of radiation measurements from the sensors, 
b)\ a radiation data quality check,
c)\ the identification of "clear sky" conditions from the radiometric data, and
d)\ data aggregation and trend analysis.

@@

As global radiation clear sky reference we are using the Haurwitz’s model, adjusted for our site with a factor of `r signif(alpha,3)` (Eq.\ \ref{eq:ahau}).
The selection of a clear sky reference model, was based on SDR observation from the period 2016 – 2021.
Where, after an iterative optimization of eight simple models (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with different factors.
We found, that Haurwitz’s model, adjusted with a factor of `r signif(alpha,3)` has the lower root mean squared error (RMSE). 
The tried models are described by @Reno2012 and tested by @Reno2016.
The iterative optimization method, for the selection of the reference is discussed by @Long2000 and @Reno2016.

@@

The running max measured value $M_{Gi} = max[\text{SDR}_{i}]$, is compared to a similar constructed value from the reference $M_{CSi} = max[\text{SDR}_{i\text{Clear Sky}}]$ (Eq.\ \ref{eq:MaxVIP}).

@@

We calculated the SDR trends, from the mean daily values of the departure from the seasonal values, for the whole time series for the three sky conditions (Table\ \ref{tab:trendtable}).

@@

Analyzing the long term trends of SDR to bins of SZA, we can see the contribution of the geometry and time in a diurnal level (Figures\ \ref{fig:szatrends}a and \ref{fig:szatrends}b). Although there is a seasonal distribution of SZA than in not presented here.

@@

Figure\ \ref{fig:cumsum}

@@

similar results with Evidence for Clear‐Sky Dimming and Brightening in Central Europe_Wild2021.pdf
include in discussion
